---
title: "hw1 problem 1"
author: "Zhe Chen"
date: "2020/9/16"
output: html_document
---

# HW1 P1

## include relevent library
```{r}
library(tidyverse)
```


## Create a data frame:

```{r}
prob1_df =
  tibble(
    ran_sample = rnorm(10),
    pos_sample = ran_sample > 0,
    char_var = LETTERS[1:10],
    lv = factor(c("S","M","L","S","M","L","S","M","L","L"))
  )
```

## Check the data frame:
```{r}
print(prob1_df)
```

## Take the mean of each variable:
```{r}
m_ran_samp = mean(prob1_df$ran_sample)
m_ran_samp
m_pos_samp = mean(prob1_df$pos_sample)
m_pos_samp
m_char_var = mean(prob1_df$char_var)
m_char_var
m_lv = mean(prob1_df$lv)
m_lv
```
From the warning output, we can know that r cannot calcuate mean of a character vector or a factor vector, since both of their data type is character, not numeric.  

## Convert the data type to numeric
```{r}
as.numeric(prob1_df$ran_sample)
as.numeric(prob1_df$pos_sample)
as.numeric(prob1_df$char_var)
as.numeric(prob1_df$lv)
```
We successfully convert the first two variables (random sample, character vector) and the last variable (level) into numeric. Logical vector can be converted in numeric since r uses "1" represent TRUE and "0" represent FALSE; factor variable can be converted also because factor represents some different stratification, although it may be meaningless;character type of data cannot be converted into numeric data.

## Apply multiplication
```{r}
as.numeric(prob1_df$pos_sample)*prob1_df$ran_sample
factor(prob1_df$pos_sample)*prob1_df$ran_sample
as.numeric((factor(prob1_df$pos_sample)))*prob1_df$ran_sample
```
From the warning, we know multiplication cannot be applied to factor data without converting to numbers. In general, multiplication can apply between numeric data and numberic data, not numeric data and character (or factor) data.





